Safe Memory Regions for Big Data Processing

### 2016-06-23 paper/type-inference.tex
incompleteness
removed constructor

\subsection{Constraints}
\label{sec:fb-constraintsem}

@@

@@

\paragraph{Properties of generated constraints}
The set of generated constraints have two interesting properties that allow us to
solve the constraints efficiently.
%
The first property is that every region variable is guaranteed to be unified with some
region constant by the constraints\footnote{
There is one special case where this does not hold: a recursive function
that calls itself in a non-terminating fashion. Such a function never
returns a value, and so the return-value can be typed as anything.
We assume that the return value of such a function is typed to be \C{unit},
which will not introduce any region variables at the call-site of such a function.}
This follows because $\FB$ does not admit uninitialized variables.
% , and the type system uniquely determines the region parameters of every value
%
The second property is that the \emph{context region constraint} $\phictxt$
occurring on the antecedent of any validity constraint is a conjunction of
outlives-constraints of the form $\pi \outlives \pi_s$ where $\pi_s$
is a static region identifier and $\pi$ is a region constant (either a formal
region parameter, or static region identifier, or open transferable region identifier).
Furthermore, if $\phictxt$ includes any conjunct $\pi \outlives \pi_s$, then
it includes every conjunct $\pi_f \outlives \pi_s$ for every $\pi_f \in \predDeltaMap(\varphi)$.

@@

\begin{enumerate}
\item Our technique for determining the set of region parameters for a recursive class
incorporates a specific heuristic, namely that the recursive occurrence of the class has
the same parameters, in the same order, as the class itself. This technique will fail, for
example. if the program uses a recursive list type whose elements alternatively come
from two different regions.
% , $R_1$ and $R_2$.
% both of which are region parameters of the class.

>>>>

\subsection{The Constraint Satisfaction Problem (CSP)}
\label{sec:fb-constraintsem}

@@

\paragraph{Properties of generated constraints}
In the sequel, we will restrict our attention to a special class of CSPs that satisfy
two interesting properties that allow us to solve the constraints efficiently.
The constraints generated our type inference algorithm satisfy these two properties.
%
The first property is that every region variable is guaranteed to be unified with some
region constant by the constraints\footnote{
There is one special case where this does not hold: a recursive function
that calls itself in a non-terminating fashion. Such a function never
returns a value, and so the return-value can be typed as anything.
We assume that the return value of such a function is typed to be \C{unit},
which will not introduce any region variables at the call-site of such a function.}
This follows because $\FB$ does not admit uninitialized variables.
% , and the type system uniquely determines the region parameters of every value
%
The second property is that the \emph{context region constraint} $\phictxt$
occurring on the antecedent of any validity constraint is a conjunction of
outlives-constraints of the form $\pi \outlives \pi_s$ where $\pi_s$
is a static region identifier and $\pi$ is a region constant (either a formal
region parameter, or static region identifier, or open transferable region identifier).
Furthermore, if $\phictxt$ includes any conjunct $\pi \outlives \pi_s$, then
it includes every conjunct $\pi_f \outlives \pi_s$ for every $\pi_f \in \predDeltaMap(\varphi)$.

@@

@@

\begin{enumerate}
\item Our technique for determining the set of region parameters for a recursive class
incorporates a specific heuristic, namely that the recursive occurrence of the class has
the same parameters, in the same order, as the class itself. This technique will fail, for
example. if the program uses a recursive list type whose elements alternatively come
from two different regions. Such a program would require the following elaboration,
which is beyond the scope of our approach:
% , $R_1$ and $R_2$.
% both of which are region parameters of the class.
\begin{tabular}{ccc}
\begin{minipage}{0.3\linewidth}
\begin{codejava}
class List
  $\extends$ $\ObjZ$
{
  $\ObjZ$ data;
  List next;
}
\end{codejava}
\end{minipage}
&
$\Rightarrow$
&
\begin{minipage}{0.5\linewidth}
\begin{codejava}
class List $\langle \rho_0, \rho_1, \rho_2 \; | \; \varphi \rangle$
  $\extends$ $\ObjZ \langle \rho_0 \rangle$
{
  $\ObjZ \langle \rho_1 \rangle$ data;
  $\C{List} \langle \rho_0, \rho_2, \rho_1 \rangle$ next;
}
\end{codejava}
\end{minipage}
\end{tabular}
